Supporting Information

### 2018-03-05 SupportingInformation.Rmd
added some comments on things Shya can work on moving forward

# Question 1 analyses for each dataset
Recall that question 1 is: Do datasets in ecology and related fields have non-Gausian copula srtructure? Do they show tail dependence distinct from that of a Gaussian copula? In particular do they show asymmetric tail dependence?

@@

@@

dev.off()

@@

>>>>

# Question 1 analyses for each dataset
Recall that question 1 is: Do datasets in ecology and related fields have non-Gausian copula structure? Do they show tail dependence distinct from that of a Gaussian copula? In particular do they show asymmetric tail dependence?

@@

<!--Shya to edit this description of the stats. Don't need subsections for each stat.-->
<!--Eventually we will need to add methods on how we use these stats, which is different for multivariate and bivariate data-->
<!--Eventually, for the multivariate data, we will need to demonstrate using a similar analysis to what is in mbsyn, that you can detect asymmetry of tail dependence using these stats - we have done this, but it needs to be adapted-->

@@

dev.off()
#DAN: have to make the plot actually appear in the Rmd output, with a caption and everything!
```

@@

Recall question 3 is: What are the consequences of non-Gaussian copula structure and tail dependence for our understanding of biology and for applications?

## Aphid count

<!--Shya to add results about skewness of spatial means-->

## Aphid first flight

<!--Shya to add results about skewness of spatial means-->

## North Sea plankton

<!--Shya to add results about skewness of spatial means-->
